Measurement Clusterization in D-optimal Designs for Bayesian Linear Inverse Problems

### 2023-05-05 latex/prelims.tex
Moved example to appendix, added questions and answers in intro.

\subsection{Bayesian Linear Inverse Problems}\label{subsec:abstract OED}
Let $\hilp$ and $\hilo$ be separable Hilbert spaces (the subscripts p
and o are for ``parameter'' and ``observation'', respectfully). Denote
$\hilo^* \simeq \hilo$ the Hilbert space of all linear functionals on
$\hilo$. Let $\fwd: \hilp \to \hilo$ the \emph{forward operator}. The
forward operator $\fwd$ is assumed linear and strongly smoothing (has
fast decaying modes --- the heat operator from section
\ref{subsec:example} is a prime example). Take a Gaussian prior
$\param \sim \pr = \normal(\prmean ,\prcov)$ with some appropriate
covariance operator $\prcov$ \cite{Stuart10} on $\hilp$. Note that
$\fwd \prcov \fwd^*$ is the prior covariance in $\hilo$
\cite{Stuart10}. As such, $\fwd \prcov \fwd^*$ is assumed invertible
--- an assumption which will be used below. Let $m$ the number of
observations taken. Observations are taken via the \emph{observation
operator}\footnote{It is common for the observation and forward
operators to be merged $\tmp := \obs \fwd$
\cite{AlexanderianGloorGhattas14}, but the analysis carried out in the
following sections requires $\fwd$ and $\obs$ are explicitly separated
similarly to \cite{attia2022stochastic, cvetkovic2023choosing}.} $\obs
\in ( \hilo^* )^m$, so that:

\begin{equation*}%\label{eq:O}
  \obs u = (\meas_1(u), \dots, \meas_m(u) )^t \in \R^m,\ u \in \hilo,
\end{equation*}
%
%
and we refer to $\meas_j, j=1,\dots,m$ as \emph{observation
vector}s. For $u \in \hilo$ and $v\in \R^m$:
%
%
\begin{align*}
  \big (\obs^*v \big ) (u) &= \langle v, \obs u \rangle_{\R^m} = \sum_{j=1}^m  v_j \meas_j(u)
  = v^t \left ( \obs u \right ) = (v^t \obs) (u),
\end{align*}
and thus:
\begin{align}\label{eq:obs*}
  \obs^*v &= \sum_{j=1}^m v_j \meas_j = v^t \obs.
\end{align}

Data is acquired via noisy observations, and we consider two types of
error terms: Spatially correlated model error is denoted $\eps' \sim
\normal(0,\modcov)$, and modeled as a centered Gaussian measure on
$\hilo$ with covariance operator $\modcov$. Observation error is
denoted $\eps \sim \normal(0, \sigma^2 I_m)$, with $I_m \in
\mathbb{R}^{m \times m}$ the identity. Both error terms and the prior
are assumed independent of each other. Thus, data is acquired via
\begin{align}\label{eq:inverse problem}
  \data := \obs (\fwd \param + \eps') + \eps = \obs \fwd \param + \obs \eps' + \eps.
\end{align}
%% \subsubsection{Error Terms}
It is easy to verify that $\obs \eps' + \eps \in \R^m$ is a centered
Gaussian random vector with covariance matrix

\begin{align}\label{eq:Sigma}
  \begin{split}
    \Sigma(\obs) :&= \mathbb{E}[ (\obs \eps' + \eps) (\obs \eps' +
      \eps)^t ]
    % 
    % 
    = \obs \modcov \obs^* + \sigma^2I_m , 
  \end{split}
\end{align}
where
\begin{align}\label{eq:modcov explained}
  \begin{split}
    [\obs \modcov \obs^*]_{ij} & = e_i^t \obs \modcov \obs^* e_j \\
    %
    %
    %
    &= \meas_i (\modcov \meas_j) \text{ (by \eqref{eq:obs*})}.
  \end{split}
\end{align}
%% and $e_j \in \R^m$ is the $j$th standard basis vector.
%% The explicit dependence on $\obs$ will be mostly dropped for
%% convenience, so $\Sigma(\obs) = \Sigma$.  Thus, for a fixed $\obs$
%% (i.e.\ a fixed set of observations), $\data = \obs \fwd \param +
%% \bar{\eps}$ with $\bar{\eps} \sim \normal(0,\Sigma)$.
Taking $\modcov = 0$ is a common practice
\cite{Tarantola05,Kaipio2006,Vogel02} and then $\Sigma = \sigma^2I_m$
is a scalar matrix and does not depend on $\obs$.

%% Taking an error model with a non-scalar covariance allows us to
%% consider model error (modeled by $\modcov$) as well as observation
%% error (modeled by $\sigma^2$). For example, say we believe our forward
%% model does not capture some small scale phenomenon.  Then we may
%% express this belief by saying $\tru = \fwd + \err$, with $\fwd$
%% depending on $\param$ and $\err$ depending on $\sspar$, with $\param
%% \perp \sspar$. We do not know much about this effect but it is
%% reasonable to assume it changes continuously in our domain. We (may
%% choose to) model it as $\normal (0, \modcov)$ and take $\modcov$ to
%% reflect the spatial (or other) variability we imagine $\err \sspar$
%% has. Such small scale phenomenon can arise as a modeling issue, where
%% we might not model the system in its entirety. It can also arise from
%% a numerical source, where our discretization of the system is not fine
%% enough to capture all small scale phenomena.
%%  In section \ref{section:non vanishing}, we will see that assuming
%% some correlation in the error mitigates the clusterization
%% phenomenon, as reported in the literature \cite{Ucinski05}.

%% \subsubsection{Dynamics and Observation Operators}\label{subsec:dynamics}
%% Rows of $\obs$ are linear functionals and we refer to these as {\it
%%   observation vector}s. Note that we cannot choose every observation
%% vector we want. For example, we may be restricted only to pointwise
%% evaluations of $\fwd \param$ by the sensors at our disposal, in which
%% case measuring, e.g., the mean $\ell(u) = \int_{\Omega}u$ of a
%% function is not possible. Thus, it is best to think of $(\obs \fwd
%% \param)_j$ as approximations to pointwise evaluations. For example, if
%% $\hilo = L^2([-\pi, \pi])$, consider $\ell_1(x) := (2\pi
%% \eps)^{-\frac{1}{2}}\exp(-\frac{x^2}{2\eps^2})$ and $\ell_2(x)
%% :=\eps^{-1}\mathbf{1}_{[-\frac{\eps}{2}, \frac{\eps}{2}]}$. Both
%% $\ell_1$ and $\ell_2$ approximate a point measurement at $0$ for small
%% $\eps$ and, crucially, $\ell_1, \ell_2 \in \hilo^*$.
%% %% It is important to note that although $\|\ell\|_1 =
%% %% \|\ell_2\|_1=1$, unfortunately $\|\ell_1\|_2^2 = (4\pi
%% %% \eps)^{-\frac{1}{2}}$ and $\|\ell_2\|_2^2 = \eps^{-1}$.

@@

\subsection{D-Optimal Designs in Infinite Dimensions}\label{subsec:D optimal design} 
A D-optimal design maximizes expected KL divergence between posterior
and prior measures, $\post$ and $\pr$. It is useful to first recall
the definition of KL divergence:% for an arbitrary prior measure:
$$
D_{KL}(\post||\pr) = \int \log \frac{\der \post}{\der \pr}(\param) \der \post(\param).
$$

For a Bayesian linear model in finite dimensions, with Gaussian prior
and Gaussian noise, a D-optimal design minimizes the determinant of
the posterior covariance matrix\footnote{The frequentist version of
the D-optimality criterion aims to minimize the determinant of the
Fisher information matrix \cite[page 16]{Ucinski05}. Thus, the
Bayesian criterion is just a regularized version of the frequentist
criterion \cite{Chaloner1995}.}. Bayesian D-optimal designs for
inverse problems on function spaces were first studied by
\cite{AlexanderianGloorGhattas14, alexanderian2018efficient}, and just like in finite dimensions,
a D-optimal design maximizes the Kullback-Leibler divergence between
posterior and prior measures.
%% For a linear inverse problem with Gaussian prior and Gaussian
%% noise, a D-optimal design minimizes an expression analogous to the
%% determinant of the posterior covariance operator
%% \cite{AlexanderianGloorGhattas14} (also \cref{thm:d optimality}
%% below).
D-optimal designs in infinite-dimensional
Hilbert spaces were investigated in
\cite{AlexanderianGloorGhattas14}. Their main result is summarized, in
the notation presented above, in the following theorem\footnote{In
\cite{AlexanderianGloorGhattas14, alexanderian2018efficient}, results
are stated for $\Sigma=I$ (implied by $\modcov = 0,\sigma^2=1$), but
the authors also mention these results hold for more general
covariance matrices \cite[p. 681]{AlexanderianGloorGhattas14}.}:
\begin{theorem}[Slightly modified Theorem 1 from \cite{AlexanderianGloorGhattas14}]\label{thm:d optimality}
  Let $\pr = \normal(\prmean,\prcov)$ be a Gaussian prior on $\hilp$
  and let $\post = \normal(\postmean,\postcov)$ the posterior measure
  on $\hilp$ for the Bayesian linear inverse problem $\data = \obs
  \fwd\param + \obs \eps' + \eps$ discussed above. Then
  \begin{align}\label{eq:objective}
    \begin{split}
      \tar( \obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
      % 
      % 
      % 
      &= \frac12 \log \det 
      ( I + \prcov^{1/2}  \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}).
    \end{split}
  \end{align}
\end{theorem}
\begin{definition}\label{def:d optimality}
  $\obs^{\star}$ is said to be \emph{D-optimal} if $\obs^{\star} =
  \argmax_{\obs} \tar(\obs)$, where entries of $\obs \in (\hilo^*)^m$ are constrained to
  some allowed set of measurement vectors in $\hilo^*$.
\end{definition}

\noindent For an intuitive understanding of Definition \ref{def:d
  optimality}, note that from \eqref{eq:postcov} and
\eqref{eq:objective}:
\begin{align*}
  \begin{split}
    \tar(\obs) &= \det ( I + \prcov^{1/2}  \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}) \\
    &= \det \Big( \prcov ( \prcov^{-1} + \fwd ^* \obs^* \Sigma^{-1} \obs \fwd) \Big )\\
    &= \det \prcov \postcov^{-1}.
  \end{split}
\end{align*}
Since $\prcov$ is constant, a D-optimal design minimizes the posterior
covariance determinant, analogously to the finite-dimensional case.

\subsection{Notation Summary}\label{subsec:notation}
  Our notation is summarized below. We let:
  \begin{itemize}
  \item $\hilp, \hilo$ Hilbert spaces.
  \item $\fwd:\hilp \to \hilo$ a linear compact operator.
  \item $\pr \sim \mathcal{N}(0, \prcov)$ prior Gaussian measure on
    $\hilp$, with prior covariance operator $\prcov:\hilp \to \hilp$.
  \item $\obs: \hilo \to \mathbb{R}^m$ observation operator, where $m
    \in \mathbb{N}$ is the number of observations taken. 
  \item $\sigma^2 \in \mathbb{R}_{+}$ observation noise variance.
  \item $\modcov$ model error covariance operator.
    %% $\data = \obs \fwd \param + \eps$, where $\eps \in
    %% \mathbb{R}^m$ isiid $\mathcal{N}(0, \sigma^2)$ noise.
  \item $\Sigma(\obs) = \obs \modcov \obs^* + \sigma^2I$. 
  \item $\post$ the posterior measure, with covariance $\postcov$.
  \item A D-optimality design criterion
    \cite{AlexanderianGloorGhattas14}:
    \begin{align*}
      \begin{split}
        \tar(\obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
        % 
        % 
        % 
        &= \frac12 \log \det ( I + \prcov^{1/2} \fwd ^* \obs^* \Sigma(\obs)^{-1} \obs
        \fwd \prcov^{1/2}).
      \end{split}
    \end{align*}
  %% \item $\{\lambda_i\}_{i=1}^\infty$ eigenvalues of $\fwd\prcov\fwd^*$
  %%   in decreasing order of magnitude.
  %% %% \item $\{\ev_i\}_{i=1}^\infty$ their corresponding eigenvectors.
  %% \item $\{\eta_i\}_{i=1}^\infty$ eigenvalues of $\obs^*\obs$.
  \end{itemize}

>>>>

\subsection{Bayesian Linear Inverse Problems}\label{subsec:abstract OED}
Let $\hilp$ and $\hilo$ be separable Hilbert spaces (the subscripts p
and o are for ``parameter'' and ``observation'', respectively). Denote
$\hilo^* \simeq \hilo$ the Hilbert space of all linear functionals on
$\hilo$. Let $\fwd: \hilp \to \hilo$ the \emph{forward operator}. The
forward operator $\fwd$ is assumed linear and strongly smoothing (has
fast decaying modes --- the heat operator of the example in Section
\ref{section:intro} is a prime example). Take a Gaussian prior $\param
\sim \pr = \normal(\prmean ,\prcov)$ with some appropriate covariance
operator $\prcov$ on $\hilp$ \cite{Stuart10}. Note that $\fwd \prcov
\fwd^*$ is the prior covariance in $\hilo$ \cite{Stuart10}. As such,
$\fwd \prcov \fwd^*$ is assumed invertible --- an assumption which
will be used below. Let $m$ the number of measurements
taken. Measurements are taken via the \emph{measurement
operator}\footnote{It is common for the measurement and forward
operators to be merged $\tmp := \obs \fwd$
\cite{AlexanderianGloorGhattas14}, but the analysis carried out in the
following sections requires $\fwd$ and $\obs$ are explicitly separated
as in \cite{attia2022stochastic, cvetkovic2023choosing}.} $\obs \in (
\hilo^* )^m$, whose entries $\meas_j, j=1,\dots,m$ are called
\emph{measurement vector}s:

\begin{equation*}%\label{eq:O}
  \obs u = (\meas_1(u), \dots, \meas_m(u) )^t \in \R^m,\ u \in \hilo.
\end{equation*}
%
%

%% For $u \in \hilo$ and $v\in \R^m$:
%% %
%% %
%% \begin{align*}
%%   \big (\obs^*v \big ) (u) &= \langle v, \obs u \rangle_{\R^m} = \sum_{j=1}^m  v_j \meas_j(u)
%%   = v^t \left ( \obs u \right ) = (v^t \obs) (u),
%% \end{align*}
%% and thus:
%% \begin{align}\label{eq:obs*}
%%   \obs^*v &= \sum_{j=1}^m v_j \meas_j = v^t \obs.
%% \end{align}

Data is acquired via noisy observations, and we consider two types of
error terms: Spatially correlated model error $\eps' \sim
\normal(0,\modcov)$ with $\modcov: \hilo \to \hilo$ a covariance
operator. Observation error is denoted $\eps \sim \normal(0, \sigma^2
I_m)$, with $I_m \in \mathbb{R}^{m \times m}$ the identity. Both error
terms and the prior are assumed independent of each other. Thus, data
is acquired via
\begin{align}\label{eq:inverse problem}
  \data := \obs (\fwd \param + \eps') + \eps = \obs \fwd \param + \obs \eps' + \eps.
\end{align}
%% \subsubsection{Error Terms}
It is easy to verify that $\obs \eps' + \eps \in \R^m$ is a centered
Gaussian random vector with covariance matrix

\begin{align}\label{eq:Sigma}
  \begin{split}
    \Sigma(\obs) :&= \mathbb{E}[ (\obs \eps' + \eps) (\obs \eps' +
      \eps)^t ]
    % 
    % 
    = \obs \modcov \obs^* + \sigma^2I_m , 
  \end{split}
\end{align}
where
\begin{align}\label{eq:modcov explained}
  \begin{split}
    [\obs \modcov \obs^*]_{ij} & = e_i^t \obs \modcov \obs^* e_j 
    %
    %
    %
    = \meas_i (\modcov \meas_j).% \text{ (by \eqref{eq:obs*})}.
  \end{split}
\end{align}
%% and $e_j \in \R^m$ is the $j$th standard basis vector.
%% The explicit dependence on $\obs$ will be mostly dropped for
%% convenience, so $\Sigma(\obs) = \Sigma$.  Thus, for a fixed $\obs$
%% (i.e.\ a fixed set of observations), $\data = \obs \fwd \param +
%% \bar{\eps}$ with $\bar{\eps} \sim \normal(0,\Sigma)$.
Taking $\modcov = 0$ is a common practice
\cite{Tarantola05,Kaipio2006,Vogel02} and then $\Sigma = \sigma^2I_m$
is a scalar matrix and does not depend on $\obs$.

%% Taking an error model with a non-scalar covariance allows us to
%% consider model error (modeled by $\modcov$) as well as observation
%% error (modeled by $\sigma^2$). For example, say we believe our
%% forward model does not capture some small scale phenomenon.  Then
%% we may express this belief by saying $\tru = \fwd + \err$, with
%% $\fwd$ depending on $\param$ and $\err$ depending on $\sspar$, with
%% $\param \perp \sspar$. We do not know much about this effect but it
%% is reasonable to assume it changes continuously in our domain. We
%% (may choose to) model it as $\normal (0, \modcov)$ and take
%% $\modcov$ to reflect the spatial (or other) variability we imagine
%% $\err \sspar$ has. Such small scale phenomenon can arise as a
%% modeling issue, where we might not model the system in its
%% entirety. It can also arise from a numerical source, where our
%% discretization of the system is not fine enough to capture all
%% small scale phenomena.  In section \ref{section:non vanishing}, we
%% will see that assuming some correlation in the error mitigates the
%% clusterization phenomenon, as reported in the literature
%% \cite{Ucinski05}.

%% \subsubsection{Dynamics and Observation
%% Operators}\label{subsec:dynamics} Rows of $\obs$ are linear
%% functionals and we refer to these as {\it observation
%% vector}s. Note that we cannot choose every observation vector we
%% want. For example, we may be restricted only to pointwise
%% evaluations of $\fwd \param$ by the sensors at our disposal, in
%% which case measuring, e.g., the mean $\ell(u) = \int_{\Omega}u$ of
%% a function is not possible. Thus, it is best to think of $(\obs
%% \fwd \param)_j$ as approximations to pointwise evaluations. For
%% example, if $\hilo = L^2([-\pi, \pi])$, consider $\ell_1(x) :=
%% (2\pi \eps)^{-\frac{1}{2}}\exp(-\frac{x^2}{2\eps^2})$ and
%% $\ell_2(x) :=\eps^{-1}\mathbf{1}_{[-\frac{\eps}{2},
%% \frac{\eps}{2}]}$. Both $\ell_1$ and $\ell_2$ approximate a point
%% measurement at $0$ for small $\eps$ and, crucially, $\ell_1, \ell_2
%% \in \hilo^*$.  %% It is important to note that although $\|\ell\|_1
%% = %% \|\ell_2\|_1=1$, unfortunately $\|\ell_1\|_2^2 = (4\pi %%
%% \eps)^{-\frac{1}{2}}$ and $\|\ell_2\|_2^2 = \eps^{-1}$.

@@

\subsection{Bayesian D-Optimal Designs in Infinite Dimensions}\label{subsec:D optimal design} 
A Bayesian D-optimal design maximizes expected KL divergence between
posterior and prior measures, $\post$ and $\pr$. It is useful to first
recall the definition of KL divergence:% for an arbitrary prior
measure:
$$
D_{KL}(\post||\pr) = \int \log \frac{\der \post}{\der \pr}(\param) \der \post(\param).
$$

The study of D-optimal designs for Bayesian linear inverse problems in
infinite dimensions was pioneered by \cite{AlexanderianGloorGhattas14,
  alexanderian2018efficient}. The main result we will make use of is
summarized (in our notation) in Theorem \ref{thm:d optimality}\footnote{In
\cite{AlexanderianGloorGhattas14, alexanderian2018efficient}, results
are stated for $\Sigma=I$ (implied by $\modcov = 0,\sigma^2=1$), but
the authors also mention these results hold for more general
covariance matrices \cite[p. 681]{AlexanderianGloorGhattas14}.}:

%% , and just like in finite dimensions, a D-optimal design maximizes
%% the Kullback-Leibler divergence between posterior and prior
%% measures For a linear inverse problem with Gaussian prior and
%% Gaussian noise, a D-optimal design minimizes an expression
%% analogous to the determinant of the posterior covariance operator
%% \cite{AlexanderianGloorGhattas14} (also \cref{thm:d optimality}
%% below).  D-optimal designs in infinite-dimensional Hilbert spaces
%% were investigated in \cite{AlexanderianGloorGhattas14}.
\begin{theorem}[Slightly modified Theorem 1 from \cite{AlexanderianGloorGhattas14}]\label{thm:d optimality}
  Let $\pr = \normal(\prmean,\prcov)$ be a Gaussian prior on $\hilp$
  and let $\post = \normal(\postmean,\postcov)$ the posterior measure
  on $\hilp$ for the Bayesian linear inverse problem $\data = \obs
  \fwd\param + \obs \eps' + \eps$ discussed above. Then
  \begin{align}\label{eq:objective}
    \begin{split}
      \tar( \obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
      % 
      % 
      % 
      &= \frac12 \log \det 
      ( I + \prcov^{1/2}  \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}).
    \end{split}
  \end{align}
\end{theorem}
\begin{definition}\label{def:d optimality}
  $\obs^{\star}$ is said to be \emph{D-optimal} if $\obs^{\star} =
  \argmax_{\obs} \tar(\obs)$, where entries of $\obs \in (\hilo^*)^m$ are constrained to
  some allowed set of measurement vectors in $\hilo^*$.
\end{definition}

For a Bayesian linear model in finite dimensions, with Gaussian prior
and Gaussian noise, a D-optimal design minimizes the determinant of
the posterior covariance matrix\footnote{The frequentist version of
the D-optimality criterion aims to minimize the determinant of the
Fisher information matrix \cite[page 16]{Ucinski05}. Thus, the
Bayesian criterion is just a regularized version of the frequentist
criterion \cite{Chaloner1995}.}. Theorem \ref{thm:d optimality} and
Definition \ref{def:d optimality} have a similar intuition:
\begin{align*}
  \begin{split}
    \tar(\obs) &= \frac12 \log \det ( I + \prcov^{1/2}  \fwd ^* \obs^* \Sigma^{-1} \obs \fwd \prcov^{1/2}) \text{ by \eqref{eq:objective}}\\
    &= \frac12 \log \det \Big( \prcov ( \prcov^{-1} + \fwd ^* \obs^* \Sigma^{-1} \obs \fwd) \Big )\\
    &= \frac12 \log \det \prcov \postcov^{-1} \text{ by \eqref{eq:postcov}} \\
    &= \frac12 \log \det \prcov -\frac12 \log \det \postcov.
  \end{split}
\end{align*}
Since $\prcov$ is constant, a D-optimal design minimizes the posterior
covariance determinant, analogously to the finite-dimensional case.

\subsection{Notation Summary}\label{subsec:notation}
  Our notation is summarized below. We let:
  \begin{itemize}
  \item $\hilp, \hilo$ Hilbert spaces.
  \item $\fwd:\hilp \to \hilo$ a linear compact operator.
  \item $\pr \sim \mathcal{N}(0, \prcov)$ prior Gaussian measure on
    $\hilp$, with prior covariance operator $\prcov:\hilp \to \hilp$.
  \item $\obs: \hilo \to \mathbb{R}^m$ measurement operator, where $m
    \in \mathbb{N}$ is the number of measurements taken.
  \item $\sigma^2 \in \mathbb{R}_{+}$ observation noise variance.
  \item $\modcov$ model error covariance operator.
    %% $\data = \obs \fwd \param + \eps$, where $\eps \in
    %% \mathbb{R}^m$ isiid $\mathcal{N}(0, \sigma^2)$ noise.
  \item $\Sigma(\obs) = \obs \modcov \obs^* + \sigma^2I$. 
  \item $\post$ the posterior measure, with covariance $\postcov$.
  \item A D-optimality design criterion
    \cite{AlexanderianGloorGhattas14}:
    \begin{align*}
      \begin{split}
        \tar(\obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
        % 
        % 
        % 
        &= \frac12 \log \det ( I + \prcov^{1/2} \fwd ^* \obs^* \Sigma(\obs)^{-1} \obs
        \fwd \prcov^{1/2}).
      \end{split}
    \end{align*}
  %% \item $\{\lambda_i\}_{i=1}^\infty$ eigenvalues of $\fwd\prcov\fwd^*$
  %%   in decreasing order of magnitude.
  %% %% \item $\{\ev_i\}_{i=1}^\infty$ their corresponding eigenvectors.
  %% \item $\{\eta_i\}_{i=1}^\infty$ eigenvalues of $\obs^*\obs$.
  \end{itemize}
